Short-term hourly forecasting for care services

### 2021-10-04 paper/paper.Rmd
Add some results...

Still to add details on skill scores and bootstrap methods...

@@

(Plots generated with theme_few - they look nice, good suggestion! Not sure how to include them in bookdown, can you help, Bahman? The plots are in the results folder for now, can either point to them from here, or I can change the Evauation script to save them somewhere else, and maybe in a different format? I guess PDF might be preferred. I will also use xtable to make a few tables of results, for now there is a CSV in the results folder. I realise that while I prepared my secript to produce point forecasts I haven't run it yet so will do this next week.)

>>>>

To compare model performance, and the significance of any apparent difference in performance, it is useful to define skill scores. Skill scores may be calculated for any metric using
\begin{equation}
     \text{Skill} = \frac{M_\text{ref} - M}{M_\text{ref} - M_\text{perf}}
\end{equation}
where $M$ is the metric's value for the method being considered, $M_\text{ref}$ is the metric's value for a reference method, and $M_\text{perf}$ is the metrics value for   the `perfect' method, which is zero in the case of RMSE and Pinball. We will use bootstrap re-sampling of skill scores to determine if apparent differences in forecast performance (i.e. positive or negative skill) are significantly different from zero [@Efron1981Bootstrap]. Here we use the best performing simple benchmark, Benchmark-2, as the reference model, and employ a block-boostrap with blocks of length 24h in order to account for temporal correlation of the underlying data.

@@

(Plots generated with theme_few - they look nice, good suggestion! Not sure how to include them in bookdown, can you help, Bahman? The plots are in the results folder for now, can either point to them from here, or I can change the Evauation script to save them somewhere else, and maybe in a different format? I guess PDF might be preferred. I realise that while I prepared my secript to produce point forecasts I haven't run it yet so will do this next week.)

## Case study

The data is portioned into training and test data, with all model development and hyper-parameter tuning performed using training data only. Data from 2014-04-01 to 2018-02-28 are used for training, and from 2018-03-01 to 2019-02-28 for testing.

(Summary of data, e.g. discussion of observations from training data/model development: long-term trend)

## Forecast evaluation

Probabilistic forecasts are evaluated following the principle of *sharpness subject to calibration*, meaning that the sharper forecast is prefered provided that it is calibrated. Mis-calibrated forecasts are unsuitable for use in decision-making so should be excluded. Calibration is evaluated visually in \@ref(fig-quantilebias), which highlights a systematic negative bias accross all probability levels in many models, with only the truncated normal and $t$ family GAMLSS models (NOtr-1, NOtr-2, Ttr-2) and iETS models showing good calibration across most probability levels. Notably, both benchmarks exhibit negative quantile bias as they struggle to capture the long term trend of increasing attendance.

```{r fig-quantilebias}
## Should reduce the number of models shown here... it's really hard to tell them appart!
knitr::include_graphics(rep("../results/QuantileBias.png"))
```

Evaluation metrics from the test period are presented in \@ref(tab-results) which are ordered by Quantile Bias. The five models identified above have a Quantile Bias of 0.014 or less, which is substantially lower than the next group of forecast with Quantile Biases of 0.037 and above, ETS(XXX) being the only exception with a value of 0.019.

```{r tab-results}
load("Results_Table.Rda")
knitr::kable(Res_sum[order(Res_sum$`Quantile Bias`)],
  caption = 'Forecast evluation for all methods on test data in decreasing order by Quantile Bias',
  digits=c(NA,3,2,2)
)
```

```{r fig-skill}
knitr::include_graphics(rep("../results/Skill_rel2bench_reduced.png"))
```

### 2021-10-04 paper/paper.tex
Add some results...

In order to assess performance of models, we track quantiles (5th, 10th, etc up to 95th quantile) and conditional expectations for 48 steps ahead for each model. The forecasts are produced every 12 hours for the holdout of 365 days in a rolling origin fashion \citep{Tashman2000}, resulting in 727 origins. Based on these values, several error measures are calculated to evaluate the performance of models in terms of specific quantiles and in terms of expectation. The latter is measured via Root Mean Squared Error (RMSE):
\begin{equation}
  \mathrm{RMSE} = \sqrt{\frac{1}{n} \sum_{j=1}^n e_j^2} .
  \label{eq:RMSE}
\end{equation}
When it comes to quantile performance, we used pinball, and all the other cool things described by Jethro.

Also see Equation \eqref{eq:RMSE}

@@

>>>>

In order to assess performance of models, we track quantiles (5th, 10th, etc up to 95th quantile) and conditional expectations for 48 steps ahead for each model. The forecasts are produced every 12 hours for the holdout of 365 days in a rolling origin fashion \citep{Tashman2000}, resulting in 727 origins. Based on these values, several error measures are calculated to evaluate the performance of models in terms of specific quantiles and in terms of expectation. The latter is measured via Root Mean Squared Error (RMSE):
\begin{equation}
  \mathrm{RMSE} = \sqrt{\frac{1}{n} \sum_{j=1}^n e_j^2} .
  \label{eq:RMSE}
\end{equation}

The objective of density forecasts it to be as sharp as possible while remaining reliable/calibrated \citep{Gneiting2007a}. A forecast is said to be sharp if the predictive distribution has a relatively small spread, indicating low uncertainty, witch is valuable to decision makers provided the forecast is calibrated.

The Pinball Score is a strictly proper score used to evaluate quantile forecasts and is the discrete form of the Continuous Rank Probability Score. It rewards sharpness and penalises mis-calibration, so measures all-round performance, however, calibration should still be verified separately. Furthermore,
The Pinball Score for an individual quantile matches the loss function minimised in quantile regression model estimation. The Pinball Score is given by
\begin{equation}
    % \text{Pinball} = 
    \frac{1}{T|\mathcal{A}|} \sum_{\alpha \in \mathcal{A}} \sum_{t=1}^T
 \left(q_{\alpha,t} - y_{t} \right)
 \left(\mathbb{1}(y_{t}\leq_{\alpha,t})-\alpha \right)
 \label{eq:pinball}
\end{equation}
where \(\mathcal{A} = {0.05,0.1,...,0.95}\) is the set of quantiles being estimated.

Calibration, also called `reliability', is the property that forecast probabilities match the observed frequency of realisations. If a forecast is calibrated, then 20\% of observations should fall below the \(\alpha=0.2\) predictive quantile (with some tolerance based on the finite sample size). This property is necessary for forecast probabilities to be used in quantitative decision-making. Calibration is typically evaluated visually using reliability diagrams, which plot the nominal coverage, \(\alpha\), against observer frequency mean(\(\mathbb{1}(y_{t}\le q_{\alpha,t})\)).

Still to add details on skill scores and bootstrap methods\ldots{}

@@

(Plots generated with theme\_few - they look nice, good suggestion! Not sure how to include them in bookdown, can you help, Bahman? The plots are in the results folder for now, can either point to them from here, or I can change the Evauation script to save them somewhere else, and maybe in a different format? I guess PDF might be preferred. I will also use xtable to make a few tables of results, for now there is a CSV in the results folder. I realise that while I prepared my secript to produce point forecasts I haven't run it yet so will do this next week.)
